Transmembrane helices are also an overlooked source of major histocompatibility complex class II epitopes and evolutionary more conserved than expected by chance

### 2021-02-11 bbbq_article.tex
Improve the conclusions

One interesting finding is that the MHC-I 
haplotype HLA-A*24:02 
present four times as much epitopes derived from SARS-CoV-2 TMHs
than expected by chance.
This may help the immune system to detect a SARS-CoV-2 infection earlier,
but we have not investigates if an effect can be found in clinical data.

>>>>

It is known that an individual's haplotype
influences the dynamics of a pathogen (see,
for example, \cite{eccleston2017host} for HIV).
The bioinformatics pipeline developed in this
study may be interesting to make in silico
predictions of a SARS-CoV-2 infection.
The most prominent example is the (MHC-I)
haplotype HLA-A*24:02,
which is predicted to present four times as much epitopes derived 
from SARS-CoV-2 TMHs than expected by chance.
This may help the immune system to detect a SARS-CoV-2 infection earlier,
and change the infection's dynamics.
